---
title: "Descriptives and Demographics"
output: 
    html_document:
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 1
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r data prep, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
# Loading packages
library(psych)
library(effects)
library(magrittr) # part of the tidyverse but must be read in on its own
library(parameters)
library(dplyr)
library(tidyr)
library(rio)
library(ggplot2)
library(corrplot)

# Functions to clean document, get data from wide to long format
source("functions/Cleaning.R")
source("functions/demographics counts.R")
source("functions/outliers.R")


# Setting global chunk options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

options(scipen = 999)

# Importing data
wide_data <- import("data/diss_main_combined_data_basic_clean.csv")

# Cleaning data using functions
long_data <- get_wrangled(wide_data)

clean_vars <- get_vars_cleaned(long_data)

clean_data <- remove_participants(clean_vars)
```

# Descriptives {.tabset .tabset-fade .tabset-pills}

## Overall

### BFI df

```{r}
clean_data_bfi %>% 
  select(where(is.numeric)) %>% 
  psych::describe()
```

### ELI df

```{r}
clean_data_eli %>% 
  select(where(is.numeric)) %>% 
  psych::describe()
```

## Normality - Histograms

### Threat measures

#### Symbolic

```{r}
hist(clean_data_bfi$symbolic_q)
```

Almost flat - if there were more response options, it may have been bi-modal. Highest point is 4 and then 1 and 3 are close to the same. Not the same as in the Pilot... the CFA may not replicate.

#### Realistic

```{r}
hist(clean_data_bfi$realistic_q)
```

Left-skewed, more similar to the Pilot than symbolic. Not concerning skew.

#### Distance - coffee

```{r}
hist(clean_data_bfi$distance_coffee)
```

Left-Skewed but with some respones at 1 and 2, should be robust enough in GLM

#### Distance - town

```{r}
hist(clean_data_bfi$distance_town)
```

Right-skewed, but really that most people responded to "2" and then it flattens out. Not a normal curve but not missing responses, should be robust enough.

#### Explicit - target

```{r}
hist(clean_data_bfi$explicit_targ)
```

Right-skewed... Different than pilot, but pilot was more flat, with slightly higher 1s and 2s (may have looked like this with more participants).

#### Explicit - group 

```{r}
hist(clean_data_bfi$explicit_group)
```

Left-skewed... same as pilot.

### BFI

#### Self

```{r}
hist(clean_data_bfi$bfi_self)
```

Trending toward bimodal for self, but normal for self and target.

#### Stereo

```{r}
hist(clean_data_bfi$bfi_stereo)
```

#### Target

```{r}
hist(clean_data_bfi$bfi_targ)
```

### ELI

#### Self

```{r}
hist(clean_data_bfi$eli_self)
```

Skewed for the self but normal for stereo and targ - interesting!

#### Stereo

```{r}
hist(clean_data_eli$eli_stereo)
```

#### Targ

```{r}
hist(clean_data_eli$eli_targ)
```

### Political Orientation

#### Overall

```{r}
hist(clean_data_bfi$pol_orient_1)
````

Right/positive-skewed, more severe than in the pilot (missing option 5). Would need to transform if used as a predictor.

#### Social 

```{r}
hist(clean_data_bfi$pol_orient_2)
````

Right/positive-skewed, more severe than the pilot (also missing) responses to 5. Would need to transform this variable.

#### Economic

```{r}
hist(clean_data_bfi$pol_orient_3)
````

Some 5 responses but minimal, very skewed, should still transform.

## Outliers - percentiles

### BFI

#### Self

```{r}
get_outlier_number(clean_data_bfi$bfi_self)
```

#### Stereo

```{r}
get_outlier_number(clean_data_bfi$bfi_stereo)
```

#### Target

```{r}
get_outlier_number(clean_data_bfi$bfi_targ)
```

### ELI

#### Self

```{r}
get_outlier_number(clean_data_eli$eli_self)
```

#### Stereo

```{r}
get_outlier_number(clean_data_eli$eli_stereo)
```

#### Target

```{r}
get_outlier_number(clean_data_eli$eli_targ)
```

### Threat measures

#### Realistic

```{r}
get_outlier_number(clean_data_bfi$realistic_q)
```

#### Symbolic

```{r}
get_outlier_number(clean_data_bfi$symbolic_q)
```

#### Distance - coffee

```{r}
get_outlier_number(clean_data_bfi$distance_coffee)
```

#### Distance - town

```{r}
get_outlier_number(clean_data_bfi$distance_town)
```

#### Explicit - target

```{r}
get_outlier_number(clean_data_bfi$explicit_targ)
```

#### Explicit - group

```{r}
get_outlier_number(clean_data_bfi$explicit_group)
```

### Political orientation

### Overall

```{r}
get_outlier_number(clean_data_bfi$pol_orient_1)
```

### Social

```{r}
outlier_ind1 <- get_outlier_number(clean_data_bfi$pol_orient_2)

orient_2_outliers <- clean_data_bfi[outlier_ind1,]
orient_2_outliers %>% 
  select(sub_id, pol_orient_2) %>% 
  unique()
```

2 outliers when removed from long-format

### Economic

```{r}
outlier_ind2 <- get_outlier_number(clean_data_bfi$pol_orient_3)

orient_3_outliers <- clean_data_bfi[outlier_ind2,]
orient_3_outliers %>% 
  select(sub_id, pol_orient_2) %>% 
  unique()
```

3 outliers when removed from long-format; one overlaps with above

*If I do analyses with political orientation, will need to remove outliers

# Demographics {.tabset .tabset-fade .tabset-pills}

## Sample size

### Overall - before cleaning

```{r}
wide_data %>% 
  select(sub_id) %>% 
  unique() %>% 
  nrow()
```

### Overall - after cleaning

```{r}
clean_data_bfi %>% 
  select(sub_id) %>% 
  unique() %>% 
  nrow()
```

### Overall - after cleaning & listwise removal

##### BFI

```{r}
# Looking at main variables in analysis
clean_data_bfi %>% 
  select(sub_id, analog_condition, target_condition, distance_coffee,
         distance_town, realistic_q, symbolic_q, explicit_targ, explicit_group,
         will_to_convo, pol_orient_1, pol_orient_2, pol_orient_3, bfi_self,
         bfi_stereo, bfi_targ) %>% 
  na.omit() %>% 
  select(sub_id) %>% 
  unique() %>% 
  nrow()
```

#### ELI

```{r}
# Looking at main variables in analysis
clean_data_eli %>% 
  select(sub_id, analog_condition, target_condition, distance_coffee,
         distance_town, realistic_q, symbolic_q, explicit_targ, explicit_group,
         will_to_convo, pol_orient_1, pol_orient_2, pol_orient_3, eli_self,
         eli_stereo, eli_targ) %>% 
  na.omit() %>% 
  select(sub_id) %>% 
  unique() %>% 
  nrow()
```

### Participants per condition

```{r}
clean_data_bfi %>% 
  select(sub_id, target_condition, analog_condition) %>% 
  unique() %>% 
  group_by(target_condition, analog_condition) %>% 
  count()
```

## Prolific vs UO N

### Overall - before cleaning

```{r}
wide_data %>% 
  select(sub_id, data_site) %>% 
  unique() %>% 
  group_by(data_site) %>% 
  count()
```

### Overall - after cleaning

```{r}
clean_data_bfi %>% 
  select(sub_id, data_site) %>% 
  unique() %>% 
  group_by(data_site) %>% 
  count()
```

## Age

```{r}
clean_data %>%
  select(sub_id, age) %>% 
  na.omit() %>% 
  summarize(mean = mean(age),
            sd = sd(age))
```

## Race

```{r}
ethnicity_counts <- clean_data_bfi %>% 
  select(sub_id, race) %>%  
  na.omit() %>% 
  unique() %>% 
  group_by(race) %>% 
  count()

dem_percent_table(ethnicity_counts)
```

*everyone responded to race demographic question

## Gender

```{r}
gender_counts <- clean_data_bfi %>% 
  select(sub_id, gender) %>%  
  na.omit() %>% 
  unique() %>% 
  group_by(gender) %>% 
  count()

dem_percent_table(gender_counts)
```

*everyone responded to gender demographic

## Education

```{r}
edu_counts <- clean_data_bfi %>% 
  select(sub_id, education) %>%  
  na.omit() %>% 
  unique() %>% 
  group_by(education) %>% 
  count()

dem_percent_table(edu_counts)
```

*Everyone responded about their education

## Parent education

```{r}
edu_parent_counts <- clean_data_bfi %>% 
  select(sub_id, parent_education) %>%  
  na.omit() %>% 
  unique() %>% 
  group_by(parent_education) %>% 
  count()

dem_percent_table(edu_parent_counts)
```

*One person did not respond about parent education: 423

## Birth country

```{r}
birth_country_counts <- clean_data_bfi %>% 
  select(sub_id, country_birth) %>% 
  na.omit() %>% 
  unique() %>% 
  group_by(country_birth) %>% 
  count()

dem_percent_table(birth_country_counts)
```

*Everyone responded about birth country

## Country raised

```{r}
raised_country_counts <- clean_data_bfi %>% 
  select(sub_id, country_raised) %>% 
  na.omit() %>% 
  unique() %>% 
  group_by(country_raised) %>% 
  count()

dem_percent_table(raised_country_counts)
```

*Everyone responded about what country they were raised in

### Follow-up years in US

```{r}
clean_data %>%
  filter(country_raised != "Raised in US") %>%
  select(sub_id, raised_follow) %>%
  unique()
```

Of those who responded that they were not primarily raised in the US, they have been in the US for at least 10 years to 35 years. Most should be able to vote and should all know about U.S. politics to have an opinion.

## Native language

```{r}
lang_counts <- language_counts <- clean_data_bfi %>% 
  select(sub_id, native_language) %>% 
  na.omit() %>% 
  unique() %>% 
  group_by(native_language) %>% 
  count()

dem_percent_table(lang_counts)
```

*Everyone responded to this question

### Native language follow-up

```{r}
clean_data_bfi %>% 
  filter(native_language == "Not English") %>% 
  select(sub_id, native_lang_follow) %>% 
  unique()
```

Of the 10 who responded that English is not their native language, they have spoken it for between 17-51 years. Not a concern about comprehension.
