---
title: "Downstream Effects"
output: 
    html_document:
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 1
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r data prep, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
# Loading packages
library(psych)
library(lme4)
library(nlme)
library(sjPlot)
library(effects)
library(magrittr) # part of the tidyverse but must be read in on its own
library(parameters)
library(dplyr)
library(tidyr)
library(rio)
library(ggplot2)
library(emmeans)
library(corrplot)
library(doParallel) 
library(doRNG)

# Functions to clean document, get data from wide to long format
source("functions/Cleaning.R")

# Setting global chunk options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

options(scipen = 999)

# Importing data
wide_data <- import("data/diss_main_combined_data_basic_clean.csv")

# wide_data_sub <- wide_data %>%
#   select(sub_id,
#          bfi_self_1:eli_self_10,
#          bfi_ster_1:eli_stereo_10,
#          bfi_targ_1:eli_targ_10)
# 
# bias_counts <- apply(wide_data_sub, 1, function(x) length(which(x=="3")))
# bias_counts <- as.data.frame(bias_counts)
# 
# total_answers <- length(wide_data_sub)
# 
# # Used the sub_ids obtained from below in function above
# bias_counts %>%
#   mutate(bias_percents = (bias_counts/total_answers)*100) %>%
#   filter(bias_percents > 50)
# 
# 
# wide_data <- wide_data[-c(12, 17, 18, 22, 24, 31, 40, 70, 78, 82, 86, 87, 99, 
#                           112, 130, 131, 144, 145, 147, 154, 165, 166, 180, 192, 
#                           216, 247, 253, 258, 265, 275, 291, 293, 313, 324, 349,
#                           362, 375, 385, 387, 409, 410, 460, 474, 483, 486), ] 

# Cleaning data using functions
long_data_bfi <- get_wrangled_bfi(wide_data)
long_data_eli <- get_wrangled_eli(wide_data)

clean_vars_bfi <- get_vars_cleaned(long_data_bfi)
clean_vars_eli <- get_vars_cleaned(long_data_eli)

clean_data_bfi <- remove_participants(clean_vars_bfi)
clean_data_eli <- remove_participants(clean_vars_eli)

# Target-level threat composite measures
clean_data_bfi %<>%    
  mutate(itt_comp = rowMeans(select(., c("realistic_q", "symbolic_q"))),
         itt_comp_gmc = itt_comp - mean(itt_comp, na.rm = TRUE))

clean_data_eli %<>%    
  mutate(itt_comp = rowMeans(select(., c("realistic_q", "symbolic_q"))),
         itt_comp_gmc = scale(itt_comp, center = T, scale = F))
```

*Both models are predicting the downstream effect of having a conversation with the target.*

# With BFI  {.tabset .tabset-fade .tabset-pills}

## Model output to pull coeffs

```{r}
bfi_stereo <- lmer(bfi_targ_pmc ~ bfi_self_pmc*itt_comp_gmc*bfi_stereo_pmc +
                     (bfi_self_pmc + bfi_stereo_pmc | sub_id), data = clean_data_bfi)
summary(bfi_stereo)
tab_model(bfi_stereo)
```

## Getting coefficients

```{r}
mod_coeffs <-coefficients(bfi_stereo)

cp_main <- mod_coeffs$sub_id$bfi_self_pmc
threat_comp <- mod_coeffs$sub_id$`bfi_self_pmc:itt_comp_gmc`

sub_id <- clean_data_bfi %>% 
  select(sub_id, will_to_convo) %>% 
  unique()

coeffs_df <- cbind(sub_id, cp_main, threat_comp)

coeffs_df %<>% 
  mutate(will_to_convo = as.numeric(dplyr::recode(will_to_convo,
                       `0 minutes` = "1",
                       `15 minutes` = "2",
                       `30 minutes` = "3",
                       `45 minutes` = "4",
                       `60 minutes` = "5")))
```

## Models predicting downstream 

### Main Effect

```{r}
# Singularities with so many in the models, so will do individual models
downstream_main <- lm(will_to_convo ~ cp_main, data = coeffs_df)
summary(downstream_main)
```

### Interaction

```{r}
# Singular; so did not matter doing individual models; only main effect matters
# downstream_sig_int <- lm(will_to_convo ~ threat_comp, data = coeffs_df)
# summary(downstream_sig_int)
```

## Visualization

```{r}
ggplot(coeffs_df, aes(cp_main, will_to_convo)) +
  geom_smooth(method = "lm",
              colour = "black") +
  theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  labs(y = "Time willing to converse \n(1 = None; 5 = 60 Minutes)",
       x = "Projection coefficients (BFI)")
                                        
```

# With ELI {.tabset .tabset-fade .tabset-pills}

## Model (from ELI test of residual counter-projection)

```{r}
eli_mod<- lmer(eli_targ_pmc ~ eli_self_pmc*itt_comp_gmc*eli_stereo_pmc + 
                     (0 + eli_self_pmc + eli_stereo_pmc | sub_id), 
                   data = clean_data_eli)
summary(eli_mod)
```

## Getting coefficients

```{r}
eli_mod_coeffs <- coefficients(eli_mod)

cp_main_eli <- eli_mod_coeffs$sub_id$eli_self_pmc
threat_comp_eli <- eli_mod_coeffs$sub_id$`eli_self_pmc:itt_comp_gmc`

sub_id_eli <- clean_data_eli %>% 
  select(sub_id, will_to_convo) %>% 
  unique()

coeffs_df_eli <- cbind(sub_id_eli, cp_main_eli, threat_comp_eli)

coeffs_df_eli %<>% 
  mutate(will_to_convo = as.numeric(dplyr::recode(will_to_convo,
                       `0 minutes` = "1",
                       `15 minutes` = "2",
                       `30 minutes` = "3",
                       `45 minutes` = "4",
                       `60 minutes` = "5")))
```

## Models predicting downstream 

### Main Effect

```{r}
# Singularities with so many in the models, so will do individual models
downstream_main_eli <- lm(will_to_convo ~ cp_main_eli, data = coeffs_df_eli)
summary(downstream_main_eli)
```

### Interaction

```{r}
# Singular; so did not matter doing individual models; only main effect matters
# mod_threat_eli <- lm(will_to_convo ~ threat_comp_eli, data = coeffs_df_eli)
# summary(mod_threat_eli)
```

## Visualization  {.tabset .tabset-fade .tabset-pills}

```{r}
ggplot(coeffs_df_eli, aes(cp_main_eli, will_to_convo)) +
  geom_smooth(method = "lm",
              colour = "black") +
  theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  labs(y = "Time willing to converse \n(1 = None; 5 = 60 Minutes)",
       x = "Projection coefficients (ELI)")
                                        
```
