---
title: "Residual Counter-Projection"
output: 
    html_document:
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 1
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r data prep, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
# Loading packages
library(psych)
library(lme4)
library(nlme)
library(sjPlot)
library(effects)
library(magrittr) # part of the tidyverse but must be read in on its own
library(parameters)
library(dplyr)
library(tidyr)
library(rio)
library(ggplot2)
library(emmeans)
library(corrplot)

# Functions to clean document, get data from wide to long format
source("functions/Cleaning.R")

# Setting global chunk options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

options(scipen = 999)

# Importing data
wide_data <- import("data/diss_main_combined_data_basic_clean.csv")

# Cleaning data using functions
long_data_bfi <- get_wrangled_bfi(wide_data)
long_data_eli <- get_wrangled_eli(wide_data)

clean_vars_bfi <- get_vars_cleaned(long_data_bfi)
clean_vars_eli <- get_vars_cleaned(long_data_eli)

clean_data_bfi <- remove_participants(clean_vars_bfi)
clean_data_eli <- remove_participants(clean_vars_eli)

clean_data_bfi %<>%    
  mutate(itt_comp = rowMeans(select(., c("realistic_q", "symbolic_q"))),
         itt_comp_gmc = scale(itt_comp, center = T, scale = F))

clean_data_eli %<>%    
  mutate(itt_comp = rowMeans(select(., c("realistic_q", "symbolic_q"))),
         itt_comp_gmc = scale(itt_comp, center = T, scale = F))
```

# Models for comparison

## BFI no stereo 
```{r}
bfi_nostereo_comp <- lmer(bfi_targ_pmc ~ bfi_self_pmc*itt_comp_gmc +
                     (bfi_self_pmc | sub_id), data = clean_data_bfi)
tab_model(bfi_nostereo_comp)

bfi_nostereo_targ <- lmer(bfi_targ_pmc ~ bfi_self_pmc*target_condition +
                     (bfi_self_pmc | sub_id), data = clean_data_bfi)
```

## ELI no stereo

```{r}
comp_eli_randslopes <- lmer(eli_targ_pmc ~ eli_self_pmc*itt_comp_gmc + # itt does not work as a RE; model does not converge
                     (0 + eli_self_pmc | sub_id), 
                   data = clean_data_eli)

tab_model(comp_eli_randslopes)
cond_eli_randslopes <- lmer(eli_targ_pmc ~ eli_self_pmc*target_condition + # itt does not work as a RE; model does not converge
                     (0 + eli_self_pmc | sub_id), 
                   data = clean_data_eli)
```

# Residual Counter-projection - BFI {.tabset .tabset-fade .tabset-pills}

## Only composite

### Results

```{r}
bfi_stereo_comp <- lmer(bfi_targ_pmc ~ bfi_self_pmc*itt_comp_gmc*bfi_stereo_pmc +
                     (bfi_self_pmc + bfi_stereo_pmc | sub_id), data = clean_data_bfi)
summary(bfi_stereo_comp)
tab_model(bfi_stereo_comp)
```

### Comparison with model without stereotyping

```{r}
anova(bfi_stereo_comp, bfi_nostereo_comp)
```

### Simple Slopes

```{r}
threat_levels = list(itt_comp_gmc = c(-1.07, 0.0, 1.07))
simpslopes_bfi_stereo2 <- emtrends(bfi_stereo_comp, ~ itt_comp_gmc,
                              var ="bfi_self_pmc",
                              at = c(threat_levels))


simpslopes_bfi_stereo2
test(simpslopes_bfi_stereo2)
pairs(simpslopes_bfi_stereo2)
```

### Visualization

```{r}
bfi_stereo_comp_df <- effect("bfi_self_pmc:itt_comp_gmc",
                         xlevels = list(itt_comp_gmc = c(-1.07, 0.0, 1.07)),
                         mod = bfi_stereo_comp)

bfi_stereo_comp_df <- as.data.frame(bfi_stereo_comp_df)
bfi_stereo_comp_df$itt_comp_gmc <- as.factor(bfi_stereo_comp_df$itt_comp_gmc)

ggplot(bfi_stereo_comp_df, aes(bfi_self_pmc, fit, group = itt_comp_gmc)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = itt_comp_gmc)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  scale_linetype_manual("Target-level threat",
                        breaks = c("-1.07", "0", "1.07"), 
                       labels = c("Low",
                                  "Average",
                                  "High"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(x = "BFI responses for self",
       y = "BFI responses for target")
```

### Assumptions

```{r}
# checking normality of conditional residuals
qqnorm(residuals(bfi_stereo_comp), main="Q-Q plot for conditional residuals")

# checking the normality of the random effects (here random intercept):
qqnorm(ranef(bfi_stereo_comp)$sub_id$bfi_self_pmc,
       main="Q-Q plot for the self random effect")

qqnorm(ranef(bfi_stereo_comp)$sub_id$bfi_stereo_pmc,
       main="Q-Q plot for the stereotyping random effect")

# Checking residuals for intercept
qqnorm(ranef(bfi_stereo_comp)$sub_id$`(Intercept)`,
       main="Q-Q plot for the random intercept")

plot_model(bfi_stereo_comp, type='diag')
```

Also seems to have slight tails, basically when stereotyping is added to the model

## Only target variable

### Results

```{r}
bfi_stereo_targ <- lmer(bfi_targ_pmc ~ bfi_self_pmc*target_condition*bfi_stereo_pmc +
                     (bfi_self_pmc + bfi_stereo_pmc | sub_id), data = clean_data_bfi)
summary(bfi_stereo_targ)
tab_model(bfi_stereo_targ)
```

### Comparison with model without stereotyping

```{r}
anova(bfi_stereo_targ, bfi_nostereo_targ)
```

### Simple slopes

```{r}
targ_levels <-list(target_condition = c("CONTROL", "LOSS", "WARM"))
simpslopes_bfi_stereo_targ <- emtrends(bfi_stereo_targ, ~ target_condition,
                              var ="bfi_self_pmc",
                              at = targ_levels)


simpslopes_bfi_stereo_targ 
test(simpslopes_bfi_stereo_targ)
pairs(simpslopes_bfi_stereo_targ)
```

### Visualization

```{r}
bfi_stereo_targ_df <- effect("bfi_self_pmc:target_condition",
                         xlevels = list(target_condition = c("CONTROL",
                                                             "WARM",
                                                             "LOSS")),
                         mod = bfi_stereo_targ)

bfi_stereo_targ_df <- as.data.frame(bfi_stereo_targ_df)
bfi_stereo_targ_df$target_condition <- as.factor(bfi_stereo_targ_df$target_condition)

bfi_stereo_targ_df %<>% 
  mutate(target_condition = forcats::fct_relevel(target_condition, c("CONTROL", "WARM", "LOSS")))

ggplot(bfi_stereo_targ_df, aes(bfi_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  scale_linetype_manual("Target variable",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Least threatening",
                                  "Medium threatening",
                                  "Most threatening"),
                       values = c("solid",
                                  "dashed",
                                  "dotted"))+
    labs(x = "BFI responses for self",
       y = "BFI responses for target")
```

### Assumptions

```{r}
# checking normality of conditional residuals
qqnorm(residuals(bfi_stereo_targ), main="Q-Q plot for conditional residuals")

# checking the normality of the random effects 
qqnorm(ranef(bfi_stereo_targ)$sub_id$bfi_self_pmc,
       main="Q-Q plot for the self random effect")

qqnorm(ranef(bfi_stereo_targ)$sub_id$bfi_stereo_pmc,
       main="Q-Q plot for the stereotyping random effect")

# Checking residuals for intercept
qqnorm(ranef(bfi_stereo_targ)$sub_id$`(Intercept)`,
       main="Q-Q plot for the random intercept")

plot_model(bfi_stereo_targ, type='diag')
```

Definitely a tail, but only a few points, so most likely robust; stereo is the worst, may need to transform it


# Residual Counter-projection - ELI {.tabset .tabset-fade .tabset-pills}

## Threat composite only

```{r}
comp_eli_stereo <- lmer(eli_targ_pmc ~ eli_self_pmc*itt_comp_gmc*eli_stereo_pmc + # itt does not work as a RE; model does not converge
                     (0 + eli_self_pmc + eli_stereo_pmc | sub_id), 
                   data = clean_data_eli) # Same as above, works with clean_data but not the smaller df specific to this analysis


summary(comp_eli_stereo)
tab_model(comp_eli_stereo,
          digits = 3)
```

### Comparing to model without stereotyping

```{r}
anova(comp_eli_randslopes, comp_eli_stereo)
```

### Simple slopes

```{r}
comp_stereo_simpslopes_eli <- emtrends(comp_eli_stereo, ~ itt_comp_gmc,
                              var ="eli_self_pmc",
                              at = threat_levels)

comp_stereo_simpslopes_eli
test(comp_stereo_simpslopes_eli)
pairs(comp_stereo_simpslopes_eli)
```

### Visualization

```{r}
comp_stereo_eli_maineffect <- effect("eli_self_pmc:itt_comp_gmc",
                         xlevels = list(itt_comp_gmc = c(-1.07, 0, 1.07)),
                         mod = comp_eli_stereo)

comp_stereo_eli_maineffect <- as.data.frame(comp_stereo_eli_maineffect)
comp_stereo_eli_maineffect$itt_comp_gmc <- as.factor(comp_stereo_eli_maineffect$itt_comp_gmc)

ggplot(comp_stereo_eli_maineffect, aes(eli_self_pmc, fit, group = itt_comp_gmc)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = itt_comp_gmc)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  scale_linetype_manual("Target-level threat",
                        breaks = c(-1.07, 0, 1.07), 
                       labels = c("Low",
                                  "Average",
                                  "High"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(x = "ELI responses for self",
       y = "ELI responses for target")
```

### Assumptions

```{r}
# checking normality of conditional residuals
qqnorm(residuals(comp_eli_stereo), main="Q-Q plot for conditional residuals")

# checking the normality of the random effects:
qqnorm(ranef(comp_eli_stereo)$sub_id$eli_self_pmc,
       main="Q-Q plot for the self random effect")

# looking at random effect for stereo:
qqnorm(ranef(comp_eli_stereo)$sub_id$eli_stereo_pmc,
       main="Q-Q plot for the self random effect")

plot_model(comp_eli_stereo, type='diag')
```

Heavy tail and outliers?

## Targ condition

```{r}
cond_eli_stereo <- lmer(eli_targ_pmc ~ eli_self_pmc*eli_stereo_pmc*target_condition + # itt does not work as a RE; model does not converge
                     (0 + eli_self_pmc + eli_stereo_pmc | sub_id), 
                   data = clean_data_eli) # Same as above, works with clean_data but not the smaller df specific to this analysis


summary(cond_eli_stereo)
tab_model(cond_eli_stereo,
          digits = 3)
```

### Comparing to model without stereotyping

```{r}
anova(cond_eli_randslopes, cond_eli_stereo)
```

### Simple Slopes

```{r}
simpslopes_eli_stereo_cond <- emtrends(cond_eli_stereo, ~ target_condition,
                              var ="eli_self_pmc",
                              at = targ_levels)


simpslopes_eli_stereo_cond
pairs(simpslopes_eli_stereo_cond)
```

### Visualization

```{r}

# interactions::interact_plot(compcond_eli_stereo, pred = eli_self_pmc, modx = itt_comp_gmc, mod2 = target_condition, interval = TRUE)

eli_stereo_cond <- effect("eli_self_pmc:target_condition",
                         xlevels = list(target_condition = c("CONTROL",
                                                             "WARM",
                                                             "LOSS")),
                         mod = cond_eli_stereo)

eli_stereo_cond <- as.data.frame(eli_stereo_cond)
eli_stereo_cond$target_condition <- as.factor(eli_stereo_cond$target_condition)

eli_stereo_cond %<>% 
  mutate(target_condition = forcats::fct_relevel(target_condition, c("CONTROL", "WARM", "LOSS")))

target_labels <- c("CONTROL" = "Control target",
                   "WARM" = "Warm target",
                   "LOSS" = "Loss target")

ggplot(eli_stereo_cond, aes(eli_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  scale_linetype_manual("Target Variable",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Least threatening",
                                  "Medium threatening",
                                  "High threatening"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs( x = "ELI responses for self",
       y = "ELI responses for target")
```

### Assumptions

```{r}
# checking normality of conditional residuals
qqnorm(residuals(cond_eli_stereo), main="Q-Q plot for conditional residuals")

# checking the normality of the random effects:
qqnorm(ranef(cond_eli_stereo)$sub_id$eli_self_pmc,
       main="Q-Q plot for the self random effect")

# looking at random effect for stereo:
qqnorm(ranef(cond_eli_stereo)$sub_id$eli_stereo_pmc,
       main="Q-Q plot for the self random effect")

plot_model(cond_eli_stereo, type='diag')
```

# Checking effect of removing UO participants - BFI {.tabset .tabset-fade .tabset-pills}

## No stereotyping

### Only composite

```{r}
data_bfi_prolific <- clean_data_bfi %>% 
  filter(data_site != "uo") %>% 
  select(sub_id, bfi_number, bfi_targ_pmc, bfi_self_pmc, itt_comp_gmc,
         target_condition, bfi_targ, bfi_self, bfi_stereo, bfi_stereo_pmc) %>% 
  unique() %>% 
  na.omit() 

bfi_nostereo_comp_pro <- lmer(bfi_targ_pmc ~ bfi_self_pmc*itt_comp_gmc +
                     (bfi_self_pmc | sub_id), data = data_bfi_prolific)
summary(bfi_nostereo_comp_pro)
tab_model(bfi_nostereo_comp_pro)
```

Did not change

#### Simple Slopes

```{r}
bfi_nostereo_comp_pro <- emtrends(bfi_nostereo_comp_pro , ~ itt_comp_gmc,
                              var ="bfi_self_pmc",
                              at = c(threat_levels))


bfi_nostereo_comp_pro
```

Did not change

### Target variable

```{r}
bfi_nostereo_targ_pro <- lmer(bfi_targ_pmc ~ bfi_self_pmc*target_condition +
                     (bfi_self_pmc | sub_id), data = data_bfi_prolific)
summary(bfi_nostereo_targ_pro)
tab_model(bfi_nostereo_targ_pro)
```

Did not change

#### Simple Slopes

```{r}
bfi_nostereo_targ_pro <- emtrends(bfi_nostereo_targ_pro, ~ target_condition,
                              var ="bfi_self_pmc",
                              at = targ_levels)


bfi_nostereo_targ_pro 
```

Did not change 

## Stereotyping

### Only composite

```{r}
bfi_stereo_comp_pro <- lmer(bfi_targ_pmc ~ bfi_self_pmc*itt_comp_gmc*bfi_stereo_pmc +
                     (bfi_self_pmc + bfi_stereo_pmc | sub_id), data = data_bfi_prolific)
summary(bfi_stereo_comp_pro)
tab_model(bfi_stereo_comp_pro)
```


Did not change

#### Simple Slopes

```{r}
bfi_stereo_comp_pro <- emtrends(bfi_stereo_comp_pro, ~ itt_comp_gmc,
                              var ="bfi_self_pmc",
                              at = threat_levels)


bfi_stereo_comp_pro
```

Did not change

### arget Condition

```{r}
bfi_stereo_targ_pro <- lmer(bfi_targ_pmc ~ bfi_self_pmc*target_condition*bfi_stereo_pmc +
                     (bfi_self_pmc | sub_id), data = data_bfi_prolific)
summary(bfi_stereo_targ_pro)
tab_model(bfi_stereo_targ_pro)
```

Model fails to converge with random effect for stereo; Dropping random effect for stereo, but results appear the same

#### Simple Slopes

```{r}
bfi_stereo_targ_pro <- emtrends(bfi_stereo_targ_pro, ~ target_condition,
                              var ="bfi_self_pmc",
                              at = targ_levels)


bfi_stereo_targ_pro 
```

Did not change

# Multicolinearity of predictors {.tabset .tabset-fade .tabset-pills}

```{r}
cor_bfi <- clean_data_bfi %>% 
  select(bfi_self_pmc, bfi_stereo_pmc, bfi_targ_pmc, itt_comp_gmc) %>% 
  unique() %>% 
  rename("BFI: Self" = bfi_self_pmc,
         "BFI: Stereo" = bfi_stereo_pmc,
         "BFI: Target" = bfi_targ_pmc,
         "Threat Composite" = itt_comp_gmc)

correlations_preds <- cor(cor_bfi)

corrplot(correlations_preds, 
         is.corr = TRUE, 
         #method = "number", 
         method = 'color',
         tl.cex = .85,
         tl.col = 'black',
         addgrid.col = 'white',
         addCoef.col = 'grey50')
```