---
title: "threat exploration"
output: 
    html_document:
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 1
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r data prep, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}
# Loading packages
library(psych)
library(lme4)
library(nlme)
library(sjPlot)
library(effects)
library(magrittr) # part of the tidyverse but must be read in on its own
library(parameters)
library(dplyr)
library(tidyr)
library(rio)
library(ggplot2)
library(emmeans)
library(corrplot)

# Functions to clean document, get data from wide to long format
source("functions/Cleaning.R")

# Setting global chunk options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

options(scipen = 999)

# Importing data
wide_data <- import("data/diss_main_combined_data_basic_clean.csv")

# Cleaning data using functions
long_data_bfi <- get_wrangled_bfi(wide_data)
long_data_eli <- get_wrangled_eli(wide_data)

clean_vars_bfi <- get_vars_cleaned(long_data_bfi)
clean_vars_eli <- get_vars_cleaned(long_data_eli)

clean_data_bfi <- remove_participants(clean_vars_bfi)
clean_data_eli <- remove_participants(clean_vars_eli)

clean_data_bfi %<>%    
  mutate(itt_comp = rowMeans(select(., c("realistic_q", "symbolic_q"))),
         itt_comp_gmc = scale(itt_comp, center = T, scale = F))

clean_data_eli %<>%    
  mutate(itt_comp = rowMeans(select(., c("realistic_q", "symbolic_q"))),
         itt_comp_gmc = scale(itt_comp, center = T, scale = F))
```

# Other measures of threat predicted by target variable

```{r}
data_threat_lm <- clean_data_bfi %>% 
  select(sub_id, target_condition, itt_comp, explicit_targ, explicit_group,
         distance_coffee, distance_town) %>% 
  unique()
```

## Distance - coffee

```{r}
distance_coffee_lm <- lm(distance_coffee ~ target_condition, data = data_threat_lm)
summary(distance_coffee_lm)
anova(distance_coffee_lm)
```

## Distance - town

```{r}
distance_town_lm <- lm(distance_town ~ target_condition, data = data_threat_lm)
summary(distance_town_lm)
anova(distance_town_lm)
```

## Explicit - group

```{r}
explicit_group_lm <- lm(explicit_group ~ target_condition, data = data_threat_lm)
summary(explicit_group_lm)
anova(explicit_group_lm)
```

Not sig different for explicit threat for the group; only one not sig, but also only measure not related to Jen in any way

## Explicit - target

```{r}
explicit_targ_lm <- lm(explicit_targ ~ target_condition, data = data_threat_lm)
summary(explicit_targ_lm)
anova(explicit_targ_lm)
```

# BFI

## Target condition alone

```{r}
bfi_targ <- lmer(bfi_targ_pmc ~ bfi_self_pmc*target_condition + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_targ)

tab_model(bfi_targ)
```

### Simple slopes

```{r}
bfi_targ_ss <- emtrends(bfi_targ, ~ target_condition,
                              var ="bfi_self_pmc",
                              at = list(target_condition = c("CONTROL", 
                                                             "LOSS", 
                                                             "WARM")))

bfi_targ_ss
```

### Visualization

```{r}
effects_cond_bfi <- effect("bfi_self_pmc:target_condition",
                         xlevels = list(target_condition = c("CONTROL", "LOSS", "WARM")),
                         mod = bfi_targ )

effects_cond_bfi <- as.data.frame(effects_cond_bfi)
effects_cond_bfi %<>% 
  mutate(target_condition = as.factor(forcats::fct_relevel(target_condition, c("CONTROL", "WARM", "LOSS"))))

ggplot(effects_cond_bfi, aes(bfi_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  scale_linetype_manual("Target threat condition",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Least threatening",
                                  "Moderately threatening",
                                  "Most threatening"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(x = "BFI responses for self",
       y = "BFI responses for target")
```

## Target condition alone - stereo

```{r}
bfi_targ_stereo <- lmer(bfi_targ_pmc ~ bfi_self_pmc*target_condition*bfi_stereo_pmc+ 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_targ_stereo)

tab_model(bfi_targ_stereo)
```

### Simple slopes

```{r}
bfi_targ_stereo_ss <- emtrends(bfi_targ_stereo, ~ target_condition,
                              var ="bfi_self_pmc",
                              at = list(target_condition = c("CONTROL", 
                                                             "LOSS", 
                                                             "WARM")))

bfi_targ_stereo_ss
```

### Visualization

```{r}
effects_cond_bfi_stereo <- effect("bfi_self_pmc:target_condition",
                         xlevels = list(target_condition = c("CONTROL", "LOSS", "WARM")),
                         mod = bfi_targ_stereo)

effects_cond_bfi_stereo <- as.data.frame(effects_cond_bfi_stereo)

effects_cond_bfi_stereo %<>% 
  mutate(target_condition = as.factor(forcats::fct_relevel(target_condition, c("CONTROL", "WARM", "LOSS"))))

ggplot(effects_cond_bfi_stereo, aes(bfi_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  scale_linetype_manual("Target threat condition",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Least threatening",
                                  "Moderately threatening",
                                  "Most threatening"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(x = "BFI responses for self",
       y = "BFI responses for target")
```

## Target condition x composite

```{r}
bfi_targ_comp <- lmer(bfi_targ_pmc ~ bfi_self_pmc*itt_comp_gmc*target_condition + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_targ_comp)

tab_model(bfi_targ_comp,
          digits = 3)
```

Results indicate that the main effect of the target-level threat composite goes away when we include threat condition. There is a main effect of condition on projection for both contrasts. There is also an interaction of target condition and the the threat composite for the contrast comparing the warm target to the control.

### Simple Slopes

```{r}
bfi_targ_comp_simpslopes_int <- emtrends(bfi_targ_comp, ~ itt_comp_gmc*target_condition,
                              var = "bfi_self_pmc",
                              at = list(target_condition = c("CONTROL", 
                                                             "LOSS", 
                                                             "WARM"),
                                        itt_comp_gmc = c(-1.07, 0.0, 1.07)))

bfi_targ_comp_simpslopes_int
```

### Visualization

```{r}
bfi_targ_comp_int_viz <- effect("bfi_self_pmc:itt_comp_gmc:target_condition",
                         xlevels = list(itt_comp_gmc = c(-1.07, 0.0, 1.07),
                                        target_condition = c("CONTROL",
                                                             "WARM",
                                                             "LOSS")),
                         mod = bfi_targ_comp)

bfi_targ_comp_int_viz <- as.data.frame(bfi_targ_comp_int_viz)
bfi_targ_comp_int_viz$itt_comp_gmc <- as.factor(bfi_targ_comp_int_viz$itt_comp_gmc)
bfi_targ_comp_int_viz$target_condition <- as.factor(bfi_targ_comp_int_viz$target_condition)

threat_labels <- c("-1.07" = "Low target \n level threat",
                   "0" = "Average target \n level threat",
                   "1.07" = "High target \n level threat")

ggplot(bfi_targ_comp_int_viz, aes(bfi_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  facet_wrap(~itt_comp_gmc,
             labeller = labeller(itt_comp_gmc = threat_labels)) +
  scale_linetype_manual("Target condition",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Control",
                                  "Warm",
                                  "Loss"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(title = "Projection by target-level threat and target condition",
         subtitle = "Using the BFI",
       x = "BFI responses for self",
       y = "BFI responses for target")
```

## Target condition x composite - stereotyping

```{r}
bfi_targ_comp_stereo <- lmer(bfi_targ_pmc ~ bfi_self_pmc*itt_comp_gmc*target_condition*bfi_stereo_pmc + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_targ_comp_stereo)

tab_model(bfi_targ_comp_stereo,
          digits = 3)
```

Results indicate that the main effect of the target-level threat composite goes away when we include threat condition. There is a main effect of condition on projection for both contrasts. There is also an interaction of target condition and the the threat composite for the contrast comparing the warm target to the control.

### Simple Slopes

```{r}
bfi_targ_comp_simpslopes_int_stereo <- emtrends(bfi_targ_comp_stereo, ~ itt_comp_gmc*target_condition,
                              var = "bfi_self_pmc",
                              at = list(target_condition = c("CONTROL", 
                                                             "LOSS", 
                                                             "WARM"),
                                        itt_comp_gmc = c(-1.07, 0.0, 1.07)))

bfi_targ_comp_simpslopes_int_stereo
```

### Visualization

```{r}
bfi_targ_comp_int_viz_stereo <- effect("bfi_self_pmc:itt_comp_gmc:target_condition",
                         xlevels = list(itt_comp_gmc = c(-1.07, 0.0, 1.07),
                                        target_condition = c("CONTROL",
                                                             "WARM",
                                                             "LOSS")),
                         mod = bfi_targ_comp_stereo)

bfi_targ_comp_int_viz_stereo <- as.data.frame(bfi_targ_comp_int_viz_stereo)
bfi_targ_comp_int_viz_stereo$itt_comp_gmc <- as.factor(bfi_targ_comp_int_viz_stereo$itt_comp_gmc)
bfi_targ_comp_int_viz_stereo$target_condition <- as.factor(bfi_targ_comp_int_viz_stereo$target_condition)

threat_labels <- c("-1.07" = "Low target \n level threat",
                   "0" = "Average target \n level threat",
                   "1.07" = "High target \n level threat")

ggplot(bfi_targ_comp_int_viz_stereo, aes(bfi_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  facet_wrap(~itt_comp_gmc,
             labeller = labeller(itt_comp_gmc = threat_labels)) +
  scale_linetype_manual("Target condition",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Control",
                                  "Warm",
                                  "Loss"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(title = "Projection by target-level threat and target condition",
         subtitle = "Using the BFI; After accounting for stereotyping",
       x = "BFI responses for self",
       y = "BFI responses for target")
```

## Distance

### Coffee alone

```{r}
bfi_coffee <- lmer(bfi_targ_pmc ~ bfi_self_pmc*distance_coffee + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_coffee)

tab_model(bfi_coffee)

bfi_coffee_a <- lmer(bfi_targ_pmc ~ bfi_self_pmc*distance_coffee*analog_condition + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_coffee_a)

tab_model(bfi_coffee_a)
```

#### Model comparison with threat composite

```{r}
# threat composite model for comparison
bfi_nostereo_comp <- lmer(bfi_targ_pmc ~ bfi_self_pmc*itt_comp_gmc +
                     (bfi_self_pmc | sub_id), data = clean_data_bfi)

anova(bfi_nostereo_comp, bfi_coffee) 
```

Though distance in the coffee shop does interact, the model fit is better for the threat composite using the ITT due to smaller values on th eAIC, BIC, and deviance. However, they are not significantly different on the chi-square.

### Coffee x target condition

```{r}
bfi_coffee2 <- lmer(bfi_targ_pmc ~ bfi_self_pmc*distance_coffee*target_condition + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_coffee2)

tab_model(bfi_coffee2)
```

No interaction 

### Town alone

```{r}
bfi_town <- lmer(bfi_targ_pmc ~ bfi_self_pmc*distance_town + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_town)

tab_model(bfi_town)
```

#### Model comparison with threat composite

```{r}
anova(bfi_nostereo_comp, bfi_town) 
```

```{r}
anova(bfi_town, bfi_coffee) 
```

The threat composite has the better fit than the town measure, and the coffee measure has a better fit than the town measure as well.

### Town x target condition

```{r}
bfi_town2 <- lmer(bfi_targ_pmc ~ bfi_self_pmc*distance_town*target_condition + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_town2)

tab_model(bfi_town2)
```

No interaction and the effect of town actually goes away after accounting for target condition. No surprising since the conditions were manipulated to be different based on threat

## Explicit threat

### Group-level

```{r}
bfi_explicit_g <- lmer(bfi_targ_pmc ~ bfi_self_pmc*explicit_group + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_explicit_g)

tab_model(bfi_explicit_g)
```

Though it does not predict conditions, group threat still leads to counter-projection on its own.

#### Model comparison with threat composite

```{r}
anova(bfi_nostereo_comp, bfi_explicit_g) 
```

However, it has less fit than the composite measure related to the target.

### Group x target condition

```{r}
bfi_explicit_gc <- lmer(bfi_targ_pmc ~ bfi_self_pmc*explicit_group*target_condition + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_explicit_gc)

tab_model(bfi_explicit_gc)
```

Not suprisingly, there is not interaction with condition. Also, when threat is accounted for at the target-level through target condition, the main effect of explicit threat at the group-level goes away.

### Target-level

```{r}
bfi_explicit_t <- lmer(bfi_targ_pmc ~ bfi_self_pmc*explicit_targ + 
                     (bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_explicit_t)

tab_model(bfi_explicit_t)
```

#### Model comparison with threat composite

##### With the composite

```{r}
anova(bfi_nostereo_comp, bfi_explicit_t) 
```

These models are near identical in all criteria - further supporting my previous belief that my scale is definitely measuring target-level threat. Plus, these are the best fitting of the threat scales we used in explaining counter-projection.

##### With the explicit group-level

```{r}
anova(bfi_explicit_g, bfi_explicit_t) 
```

Target-level is a better fit than group-level.

### Target-level x target condition

```{r}
bfi_explicit_tc <- lmer(bfi_targ_pmc ~ bfi_self_pmc*explicit_targ*target_condition + 
                     (0 + bfi_self_pmc | sub_id), 
                   data = clean_data_bfi) 

summary(bfi_explicit_tc)

tab_model(bfi_explicit_tc)
```

Unlike with the composite measure, the explicit targ measure remains significant, but not all the the contrasts for the main effect of target condition are significant.

# ELI

## Target condition only

```{r}
eli_1c <- lmer(eli_targ_pmc ~ eli_self_pmc*target_condition +
                     (0 + eli_self_pmc | sub_id), 
                   data = clean_data_eli) 

summary(eli_1c)

tab_model(eli_1c)
```

### Simple Slopes

```{r}
eli_targ_ss <- emtrends(eli_1c, ~ target_condition,
                              var ="eli_self_pmc",
                              at = list(target_condition = c("CONTROL", 
                                                             "LOSS", 
                                                             "WARM")))

eli_targ_ss 
```

### Visualization

```{r}
eli_targ_effects <- effect("eli_self_pmc:target_condition",
                         xlevels = list(target_condition = c("CONTROL",
                                                             "WARM",
                                                             "LOSS")),
                         mod = eli_1c)

eli_targ_effects <- as.data.frame(eli_targ_effects)
eli_targ_effects$target_condition <- as.factor(eli_targ_effects$target_condition)

eli_targ_effects %<>% 
  mutate(target_condition = as.factor(forcats::fct_relevel(target_condition, c("CONTROL", "WARM", "LOSS"))))


ggplot(eli_targ_effects, aes(eli_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  scale_linetype_manual("Target condition",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Least threatening",
                                  "Moderately threatening",
                                  "Most threatening"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(x = "ELI responses for self",
       y = "ELI responses for target")
```

## Target condition only - stereotyping

```{r}
eli_1c_stereo <- lmer(eli_targ_pmc ~ eli_self_pmc*target_condition*eli_stereo_pmc +
                     (0 + eli_self_pmc | sub_id), 
                   data = clean_data_eli) 

summary(eli_1c_stereo)

tab_model(eli_1c_stereo)
```

### Simple Slopes

```{r}
eli_targ_stereo_ss <- emtrends(eli_1c_stereo, ~ target_condition,
                              var ="eli_self_pmc",
                              at = list(target_condition = c("CONTROL", 
                                                             "LOSS", 
                                                             "WARM")))

eli_targ_stereo_ss 
```

### Visualization

```{r}
eli_targ_effects_stereo <- effect("eli_self_pmc:target_condition",
                         xlevels = list(target_condition = c("CONTROL",
                                                             "WARM",
                                                             "LOSS")),
                         mod = eli_1c_stereo)

eli_targ_effects_stereo <- as.data.frame(eli_targ_effects_stereo)
eli_targ_effects_stereo$target_condition <- as.factor(eli_targ_effects_stereo$target_condition)

eli_targ_effects_stereo %<>% 
  mutate(target_condition = as.factor(forcats::fct_relevel(target_condition, c("CONTROL", "WARM", "LOSS"))))


ggplot(eli_targ_effects_stereo, aes(eli_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  scale_linetype_manual("Target condition",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Least threatening",
                                  "Moderately threatening",
                                  "Most threatening"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(x = "ELI responses for self",
       y = "ELI responses for target")
```

## Condition and threat

```{r}

model1b_eli_randslopes <- lmer(eli_targ_pmc ~ eli_self_pmc*itt_comp_gmc*target_condition + 
                     (0 + eli_self_pmc | sub_id), 
                   data = clean_data_eli) # Model only works with the whole data-set (clean_data), not when filtered down to only include observations (thus none repeated) for this analysis with mod_1_data_bfi

tab_model(model1b_eli_randslopes,
          digits = 3)
```

Similiar to the BFI, but no interaction.

### Simple slopes

```{r}
eli_targ_comp_simpslopes <- emtrends(model1b_eli_randslopes, ~ itt_comp_gmc*target_condition,
                              var = "eli_self_pmc",
                              at = list(target_condition = c("CONTROL", 
                                                             "LOSS", 
                                                             "WARM"),
                                        itt_comp_gmc = c(-1.07, 0.0, 1.07)))

eli_targ_comp_simpslopes
```

### Visualization

```{r}
eli_targ_cond_int_effects <- effect("eli_self_pmc:itt_comp_gmc:target_condition",
                         xlevels = list(itt_comp_gmc = c(-1.07, 0.0, 1.07),
                                        target_condition = c("CONTROL",
                                                             "WARM",
                                                             "LOSS")),
                         mod = model1b_eli_randslopes)

eli_targ_cond_int_effects <- as.data.frame(eli_targ_cond_int_effects)
eli_targ_cond_int_effects$itt_comp_gmc <- as.factor(eli_targ_cond_int_effects$itt_comp_gmc)
eli_targ_cond_int_effects$target_condition <- as.factor(eli_targ_cond_int_effects$target_condition)

threat_labels <- c("-1.07" = "Low target \n level threat",
                   "0" = "Average target \n level threat",
                   "1.07" = "High target \n level threat")

ggplot(eli_targ_cond_int_effects, aes(eli_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  facet_wrap(~itt_comp_gmc,
             labeller = labeller(itt_comp_gmc = threat_labels)) +
  scale_linetype_manual("Target condition",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Least threatening",
                                  "Moderately threatening",
                                  "Most threatening"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(
       x = "ELI responses for self",
       y = "ELI responses for target")
```

## Condition and threat - stereotyping

```{r}

model1b_eli_randslopes_stereo <- lmer(eli_targ_pmc ~ eli_self_pmc*itt_comp_gmc*target_condition*eli_stereo_pmc + 
                     (0 + eli_self_pmc | sub_id), 
                   data = clean_data_eli) # Model only works with the whole data-set (clean_data), not when filtered down to only include observations (thus none repeated) for this analysis with mod_1_data_bfi

tab_model(model1b_eli_randslopes_stereo,
          digits = 3)
```

### Simple slopes

```{r}
eli_targ_comp_simpslopes_stereo <- emtrends(model1b_eli_randslopes_stereo, ~ itt_comp_gmc*target_condition,
                              var = "eli_self_pmc",
                              at = list(target_condition = c("CONTROL", 
                                                             "LOSS", 
                                                             "WARM"),
                                        itt_comp_gmc = c(-1.07, 0.0, 1.07)))

eli_targ_comp_simpslopes_stereo
```

### Visualization

```{r}
eli_targ_cond_int_effects_stereo <- effect("eli_self_pmc:itt_comp_gmc:target_condition",
                         xlevels = list(itt_comp_gmc = c(-1.07, 0.0, 1.07),
                                        target_condition = c("CONTROL",
                                                             "WARM",
                                                             "LOSS")),
                         mod = model1b_eli_randslopes_stereo)

eli_targ_cond_int_effects_stereo <- as.data.frame(eli_targ_cond_int_effects_stereo)
eli_targ_cond_int_effects_stereo$itt_comp_gmc <- as.factor(eli_targ_cond_int_effects_stereo$itt_comp_gmc)
eli_targ_cond_int_effects_stereo$target_condition <- as.factor(eli_targ_cond_int_effects_stereo$target_condition)

threat_labels <- c("-1.07" = "Low target \n level threat",
                   "0" = "Average target \n level threat",
                   "1.07" = "High target \n level threat")

ggplot(eli_targ_cond_int_effects_stereo, aes(eli_self_pmc, fit, group = target_condition)) +
  geom_smooth(method = "lm", 
                size = .7, 
                se = FALSE,
                colour = "black", 
                aes(linetype = target_condition)) +
    theme_minimal(base_size = 13) +
    theme(legend.key.size = unit(1, "cm")) +
  facet_wrap(~itt_comp_gmc,
             labeller = labeller(itt_comp_gmc = threat_labels)) +
  scale_linetype_manual("Target condition",
                        breaks = c("CONTROL", "WARM", "LOSS"), 
                       labels = c("Least threatening",
                                  "Moderately threatening",
                                  "Most threatening"),
                       values = c("solid",
                                  "dashed",
                                  "dotted")) +
    labs(
       x = "ELI responses for self",
       y = "ELI responses for target")
```